Calibrating the pixel-level Kepler imaging data with a causal data-driven model \\

### 2015-02-25 cpm.tex
up to page 12 - that's how far I have read it in detail.

Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{mn}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{mn}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{mn}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star.
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any transit information. Therefore, it can be regarded as a light curve without transit signal. 
Based on this idea, 
  we can construct the ``\name\ flux'' to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

\subsection{Hyper-parameters}
In the description of \name, 
  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run cross-validation on every single stars to optimize the performance of \name.
But optimizing in this 4-dimensional space is expensive, 
  especially in \name\ we need to solve thousands of linear system with thousands of parameters. 
Therefore, in this paper, 
  we just set a general set of hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without highly variability. 
To show how this general set of hyper-parameters performs, 
  here we present a typical comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}. 
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
  than from the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout rest of the paper 
  to show the general performance of \name.

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017}
\caption{\label{hyperparameter} Comparsion between default and optimized hyper-parameters. 
In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
\name\ prediction of optimized hyper-parameters is in green line. 
The middle panel shows the CPM flux of the optimized hyper-parameters, 
while CPM flux of the default hyper-parameters is in the bottom panel, 
the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
The optimized hyper-parameter performs better than the default one, but the results from both situation are close. }
\end{figure}

>>>>

Once we have obtained the parameters $a_{mnm'}$ and $b_{mnv}$ corresponding to a particular data point $I_{mn}$,
  we can make a \emph{prediction} $I^{\ast}_{mn}$ for the intensity at that pixel.
By construction of our objective function, this is truly a prediction,
  in the sense that the optimization (or solve) that produced the parameters
  (and thus the prediction)
  did not make use of $I_{mn}$ itself,
  or even any of the pixel values that are nearby in angle or time
  (as described above).
  With all the predicted pixel values $I^{\ast}_{mn}$ of the target star,  
  our new stellar flux estimates,
  what we will call the ``\name\ prediction'',
  is constructed from the \name\ pixels
  in precisely the same way as the official \Kepler\ SAP photometry
  is constructed from the Target Pixel Files.
That is, we perform a weighted sum of \name\ predicted pixels $I^{\ast}_{mn}$ with weights $w_m$,
  all of which are either zero or unity,
  and we adopt precisely the same weight assignments as are adopted in the SAP photometry;
  in equations, the flux estimate $S_n$ at time $t_n$ of the target star is given by
\begin{eqnarray}
S_n = \sum_m w_m\,I^{\ast}_{mn}
\quad ,
\end{eqnarray}
where the sum is over the $M$ pixels that are associated with the target star \Bernhard{if the sum is only over the pixels of the target star, then all $w_m$ are equal to 1 and they can be dropped}.
As we have noted above and below, these photometric estimators are not optimal for any purpose,
  but improving them is beyond the scope of this project.

It is worth to mention that the \name\ prediction $S_{n}$ is constructed from pixels without any information about transits in the target star.\Bernhard{changed this --- I didn't understand it} Therefore, it can be regarded as a light curve without transit signal. 
Based on this idea, 
  we can construct the ``\name\ flux'' (where the inverted commas indicate that it is not a flux in the sense that stellar variability is not preserved) to be the relative residual between \name\ prediction and SAP Flux $F_{n}$
\begin{eqnarray}
\delta_{n}&\equiv&\frac{F_{n} - S_{n}}{S_{n}}
\quad .
\end{eqnarray}
The \name\ flux is 
In some sense, it is this relative residual that contains the exoplanet transit signals we seek. 
That is, a transit creates a negative residual away from the prediction, 
  and the amount of relative residual is just the fraction of the light eclipsed by the planet (the transit depth).

\subsection{Hyper-parameters}
In the description of \name, 
  we introduce 4 hyper-parameters---number of predictor stars Q (or number of predictor pixels P), 
  number of autoregressive components S, and the two regularization strength $\lambda_{a}$ and $\lambda_{b}$.
To set these 4 hyper-parameters, 
  in principle we need to run cross-validation on every single star to optimize the performance of \name.
But optimizing in this 4-dimensional space is expensive, 
  especially in \name\ we need to solve thousands of linear systems with thousands of parameters. 
Therefore, in this paper, 
  we just set a general set of ``default'' hyper-parameters ($P=4000$, $Q=3$, $\lambda_a=1e5$, $\lambda_a=1e5$), 
  which works well in most of the stars without highly variability. 
To show how this general set of hyper-parameters performs, 
  here we present a typical comparison between optimized and default hyper-parameters 
  in Fig~\ref{hyperparameter}.\Bernhard{maybe explain somewhere how SNR is calculated}  
We can see that, in Fig~\ref{hyperparameter}, 
  there is less variation in the \name\ flux from optimized hyper-parameters (green points in second panel) 
  than from the default one (red points in the bottom panel). 
In addition, the optimized flux has higher signal to noise ratio of the known transit than the default. 
However, the performance of default hyper-parameters is acceptable 
  and we will use this set of hyper-parameters throughout rest of the paper 
  to show the general performance of \name.

\begin{figure}[htb]
\centering
\includegraphics[width=\columnwidth]{compare_10187017}
\caption{\label{hyperparameter} Comparison between default and optimized hyper-parameters. 
In the top panel, SAP flux is plotted in black, \name\ prediction of default hyper parameters is in red line, 
\name\ prediction of optimized hyper-parameters is in green line. 
The middle panel shows the CPM flux of the optimized hyper-parameters, 
while CPM flux of the default hyper-parameters is in the bottom panel, 
the two vertical blue lines indicate the location of the transit signal, and signal to noise ratio is calculated in both situation. 
The optimized hyper-parameter performs better than the default one, but the results from both situation are close.}
\end{figure}
